\chapter*{Acknowledgments} 

Thanks to \textbf{Victoria Ho} for proof-reading this book and avoiding a grammatical carnage.

Thanks to \textbf{Lo\"{i}c Petit} for generously sharing his expert knowledge of the CPS-1 and the CPS-2. The section about the CPS-A and CPS-B graphic ASICs would not have been possible without the extensive documentation he produced. He also volunteered to proofread the multiple drafts of this book and suggested many important improvements. His contribution was invaluable.

The other giant upon whose shoulders this book stands is \textbf{Upsilandre}. He spent a considerable amount of time explaining Pixel Aspect Ratio and spotted many mistakes during proofreading. He conducted and shared the result of many researches not only on the CPS-1 but also on the X68000. The articles and methodology to explore Capcom ports he shared on \href{https://www.gamopat-forum.com}{gamopat-forum.com} were particularly insightful.

Thanks to \textbf{Charles MacDonald} for sharing his knowledge of the CPS-1 and for patiently explaining and re-explaining the art of tile map circuitry.

Thanks to \textbf{Ben Torkington} for making available "SF2:Platinum", his ANSI C re-write of "Street Fighter II: World Warriors".

Thanks to \textbf{STG} for his translation of Japanese articles on \href{https://shmuplations.com}{shmuplations.com}.

Thanks to \textbf{VGDensetsu} for his numerous articles about the Street Fighter series and Japanese game development in general.

Thanks to \textbf{mvs-scans.com} for their high-quality photos of the CPS-1 boards.

Thanks for \textbf{John McMaster} for his high-res scans of the CPS-A ASIC.

Thanks to the \textbf{M.A.M.E contributors} for the extensive documentation work they produced over all these years. You guys are the unsung heroes of arcade history.

Thanks to \textbf{Mike Stedman} for shedding light on some of the X68000 most obscure features and ports.