\renewcommand{\bibname}{Notes \&\ References}
\begin{thebibliography}{999}

\addcontentsline{toc}{chapter}{Notes \&\ References}

\bibitem{medal} 
\textbf{What is a Medal game?}
This is not a typo! A medal game is played with metal coins. The most famous ones are "pusher games" where the player must drops coins in a platform system. Each platform moves back and forth as automated brooms. The goal is to push coins groups past the edge of the final platform where they are rewarded to the player.    

\bibitem{planner} 
\textbf{What is a Planner?}
They were the top decision maker in a Japanese game dev team. Responsible for giving directions and making game design decisions, all other members of the team reported to them. There was usually a single Planner in charge (like Poo on 1943: The Battle of Midway) but there could be two like in Street Fighter II where both Akira Nishitani (Nin) and Akira Yasuda (Akiman) were in charge. 

\bibitem{1942-tech_specs} 
  \textbf{ "1942 Final Review Team Arcade"} (by Tyler Huberty, Greg Nazario, Isaac Simha,
  \href{https://course.ece.cmu.edu/~ece545/F16/reports/F12_Arcade1942.pdf}{link},
  2012-09-12.


\bibitem{cgm4} 
  \textbf{ "Computer Gamer Magazine \#4"} ("Coin-Op Connection" article,
  \href{https://www.youtube.com/watch?v=RxIXilYv0kM}{link},
  1985-07.

\bibitem{becareful} 
  \textbf{"Questionable figures"},
  The figures of "two years and five millions dollars" should be taken carefully. These numbers were found on a Forgotten Worlds flyer (\pageref{fw_flyer}) which also mentioned three Motorola 68000 whereas the final product only included a single one. 
  1989.

\bibitem{TheStoryOf3Dfx} 
  \textbf{ "The story of the 3dfx"} (by Fabien Sanglard),
  \href{https://fabiensanglard.net/3dfx_sst1/index.html}{link},
  2019-04-04.

\bibitem{fm_licensing} 
  \textbf{ "The Sound of Innovation: Stanford and the Computer Music Revolution"} (by Andrew J. Nelson ),
  ISBN: 978-0262028769.
  2015-03-06

\bibitem{birth_of_chunli} 
  \textbf{ "The birth of Chun-Li"} (Akiman for Archipel),
  \href{https://www.youtube.com/watch?v=RxIXilYv0kM}{link},
  2018-02.

\bibitem{mips} 
  \textbf{ "Computer Speed Claims 1980 to 1996"} (Roy Longbottom),
  \href{http://www.roylongbottom.org.uk/mips.htm}{link}.

\bibitem{dd} 
  \textbf{ "Les grands noms du jeu video, Yoshihisa Kishimoto - Enter the Double Dragon"} (Florent Gorges for Editions PixNlove),
  \href{https://www.editionspixnlove.com/les-grands-noms-du-jeu-video/289-yoshihisa-kishimoto-enter-the-double-dragon.html}{link},
  2012-07-05.


\bibitem{akiman} 
  \textbf{ "Akiman's Twitter"} (akiman),
  \href{https://twitter.com/akiman7/status/465507673572519936}{post1},
  \href{https://twitter.com/akiman7/status/309615270815731712}{post2}.
  \href{https://twitter.com/akiman7/status/386598518380453888}{post3}.

\bibitem{usgamer20160101}
  \textbf{ "Top 10 Highest-Grossing Arcade Games of All Time"} (Jaz Rignall for usgamer.net) (200,00 units: SF2 WW sold 60,000 while SF2 CE sold 140,000),
  \href{https://www.usgamer.net/articles/top-10-biggest-grossing-arcade-games-of-all-time}{link},
  2016-01-01.

\bibitem{gamerevolution20140126}
  \textbf{ "World of Warcraft Leads Industry With Nearly \$10 Billion In Revenue"} (Jonathan Leack for gamerevolution.com),
  \href{https://www.gamerevolution.com/features/13510-world-of-warcraft-leads-industry-with-nearly-10-billion-in-revenue#/slide/1}{link},
  2014-26-01.
  
\bibitem{retro}
  \textbf{"Interview with Noritaka Funamitsu"} (Retro magazine),
  \href{http://fightingstreet.com/folders/variousinfofolder/interviewfolder/sfii_funamitsu/funamitsu1.jpg}{link p1},
  \href{http://fightingstreet.com/folders/variousinfofolder/interviewfolder/sfii_funamitsu/funamitsu2.jpg}{link p2},
  \href{http://fightingstreet.com/folders/variousinfofolder/interviewfolder/sfii_funamitsu/funamitsu3.jpg}{link p3},
  .

  \bibitem{mame_cps1_video}
  \textbf{"Mame CPS-1 video driver"} (mame source code),
  \href{https://github.com/mamedev/mame/blob/e070405df99e6a5997d5a64ecd62e7161c729a9d/src/mame/video/cps1.cpp#L269}{link},
  2008-04-11.

  \bibitem{mame_driver}
  \textbf{"Mame CPS-1 driver"} (mame source code),
  \href{https://github.com/mamedev/mame/blob/e070405df99e6a5997d5a64ecd62e7161c729a9d/src/mame/drivers/cps1.cpp#L567}{link},
  2008-04-11.

  \bibitem{mame_kabuki}
  \textbf{"Kabuki z80 encryption"} (mame source code),
  \href{https://github.com/mamedev/historic-mame/blob/master/src/mame/machine/kabuki.c}{link},
  2008-04-11.


   \bibitem{cps0chipslist}
  \textbf{"Early CAPCOM Arcade Games FGPA"} (Jose Tejada),
  \href{https://github.com/jotego/jt_gng/blob/fb92e5ac0f72323638974034ad652649b6efafcb/README.md}{link},
  2020-08-05.

   \bibitem{h40}
  \textbf{"Genesis mode H40"}
  The vertical and horizontal rates in H40 are not the numbers we would get if we were to inject the dot-clock, number of dots, and number of lines in the formulas. This is because the Genesis designers wanted to have the same rate in H32 and H40 modes (59.92 Hz). The dot-clock slows down to 5.37MHz for 28 dots during HBLANK, resulting in 59.92 Hz VSYNC and 15,700 KHz HSYNC (Conversation with Upsilandre).

   \bibitem{par}
  \textbf{"Dot clock rates"} (pineight.com),
  \href{https://pineight.com/mw/page/Dot_clock_rates.xhtml}{link}.

     \bibitem{ffdevinterview}
  \textbf{"Final Fight Developer's Interview"} (capcom.com),
  \href{https://game.capcom.com/cfn/sfv/column/132673?lang=en}{link},
  2019-02-08.

       \bibitem{sf2devinterview}
  \textbf{"Street Fighter II Developer's Interview"} (capcom.com),
  \href{https://game.capcom.com/cfn/sfv/column/132595?lang=en}{link},
  2018-11-21.

     \bibitem{ar20160331}
  \textbf{"Capcom Activity Report: Akira Yasuda part 1"} (capcom.com),
  \href{https://game.capcom.com/cfn/sfv/column/112429}{link},
  2016-03-31.

     \bibitem{ar20160404}
  \textbf{"Capcom Activity Report: Akira Yasuda part 2"} (capcom.com),
  \href{https://game.capcom.com/cfn/sfv/column/112432}{link},
  2016-04-04.

     \bibitem{tgm198906}
  \textbf{"Capcom, A captive audience"} (Robin Hogg \& Dominic Handy for The Games Machine, Issue \#19),
  \href{https://archive.org/details/the-games-machine-19/page/n23/mode/2up}{link},
  1989-06-01.

     \bibitem{gamest38}
  \textbf{"Yoshiki Okamoto interview"} (Gamest Magazine \#38),
  \href{https://retrocdn.net/images/9/91/Gamest_JP_038.pdf}{link},
  1989-10-01.

     \bibitem{ffoverload}
  \textbf{"Final Fight arcade 2 players"} (arronmunroe),
  \href{https://youtu.be/HyAHGHo22Og?t=1707}{link} (Use ',' and '.' to move frame by frame)
  2013-10-12.

    \bibitem{petitCRT}
  \textbf{"DL-0921 (CPS-B-21) Video Signals Generation"} (Lo\"{i}c Petit),
  \href{https://gitlab.com/loic.petit/cps2-reverse/-/blob/master/DLs/DL-0921/doc/video-signals.md}{link},
  2020-11-29.

    \bibitem{petitSecurity}
  \textbf{"DL-0921 (CPS-B-21) Security Scheme"} (Lo\"{i}c Petit),
  \href{https://gitlab.com/loic.petit/cps2-reverse/-/blob/master/DLs/DL-0921/doc/security-scheme.md}{link}.

    \bibitem{arcadeHackerCPS1}
  \textbf{"Capcom CPS1"} (Eduardo Cruz),
  \href{http://arcadehacker.blogspot.com/2015/04/capcom-cps1-part-1.html}{part1},
  \href{http://arcadehacker.blogspot.com/2015/05/capcom-cps1-part-2.html}{part2},
  \href{http://arcadehacker.blogspot.com/2015/06/capcom-cps1-part-3.html}{part3},
  2015-04-16.
  
     \bibitem{arcadeHackerKabuki}
  \textbf{"Capcom Kabuki CPU"} (Eduardo Cruz),
  \href{ http://arcadehacker.blogspot.com/2014/11/capcom-kabuki-cpu-intro.html}{intro},
  \href{http://arcadehacker.blogspot.com/2014/11/capcom-kabuki-cpu-part-1.html}{part1},
  \href{http://arcadehacker.blogspot.com/2014/11/capcom-kabuki-cpu-part-2.html}{part2},
  \href{http://arcadehacker.blogspot.com/2014/11/capcom-kabuki-cpu-part-3.html}{part3},
  \href{http://arcadehacker.blogspot.com/2014/11/capcom-kabuki-cpu-part-4.html}{part4},
  \href{http://arcadehacker.blogspot.com/2014/11/capcom-kabuki-cpu-part-5.html}{part5},
  2014-11-16.

  \bibitem{arcadeHackerCPS1Rev}
  \textbf{"CAPCOM CPS1 Reverse Engineering"} (Eduardo Cruz),
  \href{https://www.youtube.com/watch?v=IBZc__9sM28}{link},
  2015-06-15.

    \bibitem{arcadeHackerCPS1Desuicide}
  \textbf{"CPS1 Project Update"} (Eduardo Cruz),
  \href{http://arcadehacker.blogspot.com/2015/09/project-update.html}{link},
  2015-09-19.

  \bibitem{ieee20170630}
  \textbf{"Chip Hall of Fame: Motorola MC68000 Microprocessor"} (spectrum.ieee.org),
  \href{https://spectrum.ieee.org/tech-history/silicon-revolution/chip-hall-of-fame-motorola-mc68000-microprocessor}{link},
  2017-06-30.

 \bibitem{M68000fv}
  \textbf{"Instruction prefetch on the Motorola 68000 processor"} (Jorge Cwik),
  \href{http://pasti.fxatari.com/68kdocs/68kPrefetch.html}{link},
  2005.
  

    \bibitem{cps2rebirth}
  \textbf{"CPS-2 Rebirth !!!!"} (cps2shock.retrogames.com),
  \href{https://web.archive.org/web/20060812042251/http://cps2shock.retrogames.com/wip.html}{link},
  2003-04-23.

     \bibitem{dalhsimGlitch}
  \textbf{"Street fighter 2 WW glitch invisible dhalsim"} (youtube.com Error1),
  \href{https://www.youtube.com/watch?v=qEFPzcOK_uQ}{link},
  2010-09-22.

     \bibitem{otaquest}
  \textbf{"Blending Worlds With Music: Interview With Composer Yoko Shimomura"} (otaquest.com),
  \href{https://www.otaquest.com/yoko-shimomura-interview/}{link},
  2019-12-26.

     \bibitem{fmProgramming}
  \textbf{"Programmer's Guide to Yamaha YMF 262/OPL3 FM Music Synthesizer"} (Vladimir Arnost),
  \href{https://www.fit.vutbr.cz/~arnost/opl/opl3.html}{link},
  2019-12-26.

     \bibitem{cpsBNumbers}
  \textbf{"CPS-B Number"} (tim for arcadecollection.com),
  \href{http://www.arcadecollecting.com/info/cps-b_numbers.html}{link}.

  
     \bibitem{tuhojgdv2}
  \textbf{"The Untold History of Japanese Game Developers Volume 1 (Interview: Koichi Yotsui)"} (John Szczepaniak),
  2015-11-04.

     \bibitem{gameMaestro4}
  \textbf{"Game Maestro \#4"}, \href{http://shmuplations.com/akiman/}{link}.

  \bibitem{sf2_oral_history}
  \textbf{"Street Fighter 2: Oral History"} (Matt Leone),
  \href{https://www.polygon.com/a/street-fighter-2-oral-history/}{link}.
  2014-02-03.

  \bibitem{yoko_shimomura_interview}
  \textbf{"Blending Worlds With Music: Interview With Composer Yoko Shimomura"} (OTAQUEST Editor),
  \href{https://www.otaquest.com/yoko-shimomura-interview/}{link}.
  2019-12-26.
  
    \bibitem{beep199010}
  \textbf{"BEEP! Megadrive magazine: The Women of Game Making"} (translated shmuplations.com),
  \href{https://shmuplations.com/womenofgamedesign/}{link}.
  1990-10.

    \bibitem{strider_conversion}
  \textbf{"Unfinished Strider Conversion"} (Shoestring),
  \href{https://www.jammarcade.net/strider-conversion/}{link}.
  2016-02-17.

    \bibitem{csp1_phoenix}
  \textbf{"How to Phoenix a CPS 2 PCB"} (Joe Bagadonuts),
  \href{https://www.youtube.com/watch?v=HFj8Mkw_kog}{link}.
  2015-05-18.

 \bibitem{adpcm_specs}
  \textbf{"Dialogic ADPCM Algorithm"} (Dialogic Corporation),
  \href{https://multimedia.cx/mirror/dialogic-adpcm.pdf}{link}.
  1988.



 \bibitem{sf2manual}
  \textbf{"Street Fighter 2 Manual"} (Capcom Corporation),
  \href{https://www.gamesdatabase.org/Media/SYSTEM/Arcade/Manual/formated/Street_Fighter_II--_Champion_Edition_-_1992_-_Capcom.pdf}{link}.
  1992.

 \bibitem{sf2aiengine}
  \textbf{"Street Fighter 2: The A.I engine"} (Ben Torkington),
  \href{https://sf2platinum.wordpress.com/2017/01/20/the-ai-engine}{link}.
  2017-1-20

 \bibitem{x68000spritedoubler}
  \textbf{"X68000 Sprite management"} (Koichi Yoshida),
  \href{https://yosshin4004-github-io.translate.goog/x68k/xsp/index.html?_x_tr_sl=ja&_x_tr_tl=en&_x_tr_hl=en-US}{link}.
  2021-02-25

 \bibitem{htmcc}
  \textbf{"How To Make Capcom Fighting Characters"} (Akiman, Kiki, Bengus),
  ISBN: 978-1772941364.
  2020-010-20

 \bibitem{akiman2003}
  \textbf{"Akiman, 2003 Interview from Capcom Design Works"} (Akiman, translated shmuplations),
  \href{http://shmuplations.com/akirayasuda/}{link}.
  2003

 \bibitem{YoshikiOkamotoTakashiNishiyama}
  \textbf{"A Talk Between the Creators of Street Fighter and Fatal Fury: KOF"} (Yoshiki Okamoto and Takashi Nishiyama),
  \href{https://www.youtube.com/watch?v=uqRFod7nuHo&t}{link}.
  2021-08-09

 \bibitem{sf2completefiles}
  \textbf{"Street Fighter II Complete File"} (Capcom edition),
  ISBN: 978-4257090014.
  1992-11-15

 \bibitem{sf2musics}
  \textbf{"Shoryuken..! The music of Street Fighter II"} (909originals),
  \href{https://909originals.com/2021/02/21/shoryuken-the-music-of-street-fighter-ii-how-yoko-shimomura-soundtracked-one-of-the-biggest-video-games-of-all-time/}{link}
  2021-21-02

 % \bibitem{sf2samples}
 %  \textbf{"The people who lent their voices to the characters of Street Fighter II - a thread"} (VGDensetsu),
 %  \href{https://twitter.com/vgdensetsu/status/1357040620343328771?lang=en}{link}
 %  2021-03-02

 \bibitem{x68000usage1}
  \textbf{"The CPS-1 SDK, a.k.a CAT-A"} (Akiman),
  \href{https://twitter.com/akiman7/status/1013648367837048833}{link}
  2018-07-01
  
   \bibitem{x68000usage2}
  \textbf{"The CPS-1 SDK, a.k.a CAT-A: Additional details"} (Takenori Kimoto (a.k.a KimoKimo)),
  \href{https://twitter.com/KIMOKIMO_Club/status/1013817480496627712}{link}
  2018-07-02

   \bibitem{ohXarticle}
  \textbf{"Private View: \begin{CJK}{UTF8}{min}月刊電脳倶楽部 (GEKKAN DENNŌ CLUB)\end{CJK}"} (Ted Danson),
  \href{http://thecoter.ie/2015/06/25/gekkan-denno-club/}{link}
  2015-06-25
  
     \bibitem{MSM6295_datasheet}
  \textbf{"MSM6295 datasheet} (by OKI),
  \href{https://fabiensanglard.net/sf2_sound_system/MSM6295.pdf}{link}
  
      \bibitem{smc70tech}
  \textbf{"Sony SMC-70 Microcomputer"} (by Ahm),
  \href{http://users.glitchwrks.com/~ahm/smc70/}{link}
  2011-05-19

      \bibitem{1991_retro}
  \textbf{"Capcom – Retrospective Interview"} (by https://shmuplations.com/),
  \href{https://shmuplations.com/capcom1991/}{link}
  1991


      \bibitem{sf2_music}
  \textbf{"Street Fighter II Interview Soundtrack OST"} (Yoko Shimomura),
  \href{https://www.youtube.com/watch?v=HOxN8Dzv2sw}{link}
  2017-10-28
  
        \bibitem{sf2musicsecurity}
  \textbf{"Diggin' In The Carts, Hidden Levels"} (conversation Yoko Shimomura with Manami Matsumae),
  \href{https://www.youtube.com/watch?v=Y__usQbGA5M}{link}
  2014-09-23

        \bibitem{sf2platinium}
  \textbf{"Street Fighter II Platinium Source Code"} (Ben Torkington),
  \href{https://github.com/bentorkington/sf2ww}{link}
  2021-10-10

       \bibitem{9800lines}
  \textbf{"Japan's Technical Standards: Implications for Global Trade and Competitiveness"} (John Mcintyre),
  ISBN: 978-1567200539.
  1997-02-28

       \bibitem{human68k_manual}
  \textbf{"Human68k Manual"} (gamesx.com),
\href{https://gamesx.com/wiki/doku.php?id=x68000:human68k_manual}{link}
  2019-08-27

       \bibitem{x68k_games_analysis}
  \textbf{"Le x68000 et la supériorité japonaise"} (upsilandre),
\href{https://www.gamopat-forum.com/t38282p210-le-x68000-et-la-superiorite-japonaise#3336620}{link}
  2020-12-04

       \bibitem{x68k_perfect_catalogue}
  \textbf{"X68000 Perfect Catalogue"} (by G-Walk),
ISBN: ISBN4867171018.
  2020-10-27

\end{thebibliography}