\chapter{Epilogue} 

The CPS-1 study was a passion project that took over a year to complete in my spare time. The goal was to obsessively explore the hardware, understand it down to the metal, and learn how to program it. As it is often the case, the journey took an unexpected turn and I came out of the adventure with more than I initially anticipated.

In the beginning, discovering the internals of Capcom's machine was fascinating and borderline addictive. I often found myself in the wee-hours exploring schematics or experimenting with code. The technology that unraveled confirmed the key part it played in shaping Capcom's destiny. 

The CP-System is a landmark in the history of arcades. It did a fantastic job at fighting piracy and streamline production. Its tile engine was a solid and flexible solution to developers' problems which let artists express their creativity. The audio chips allowed musicians to produce melodies rivaling with competitions.

It is when I starting studying the systems competing against the CP-System in the early 90s that an epiphany started to brew in me. 

Capcom's arch-nemesis, SNK, had built an impressive machine which surpassed the CP-System. Games were built relying exclusively on sprites without using limiting tilemaps. While the CPS-1 could display 256 sprites, the Neo-Geo could achieve 381. Each of the Neo-Geo sprites could be scaled via a shrinking technique extensively used in successful titles such as Super Sidekicks. 

The list goes on with auto-animation allowing to define-and-forget an animation, a feature used profusely in Metal Slug for the gorgeous result that made it famous, HSYNC detection which unlocked raster effects, and the proudly advertised 330 megabits capacity of its boards.

Yet, despite its hardware's shortcomings, Capcom games were able to hold their own. In several occurrences some even managed to achieve much greater success than titles running on the Neo-Geo. It was like if, past a certain point, technology did not matter that much.

As this book was coming to an end, I found myself admiring more and more the work of the people who breed life into the silicon. Yes, they had a good platform to work with but it was not a silver bullet either. These creatives slept under their desk. They courageously tracked allocations with paper and scissors, they entered pixel colors by hand, tile by tile, using a keyboard. They worked over night and passed ROM chips using string though the windows in order to meet deadlines.

This venture started with the ambition to give readers a greater appreciation for the hardware. It ends with an author having opened his eyes on the artists and designers who put a soul in the machine.

Ladies and gentlemen of Capcom, hardware engineers, software programmers, artists, musicians, and designers, all you hard work and sacrifices resulted in joy and happiness of millions. 

Thank you a thousand times. 

- Fabien Sanglard
