\chapter{People} 
\label{people}

Many people were mentioned during this book. In the early 90s, Capcom arcade division was already large with three teams working on independent titles. It can be tedious to figure out who worked on what. Here is a summary.

\textbf{Kenzo Tsujimoto}, (\begin{CJK}{UTF8}{min}辻本憲三\end{CJK}): Founded Irem in 1974, a company that would go on making many games, including the legendary R-Type and Kung-Fu Master. Forced out over revenues following the release of IPM Invaders, he founded Capcom which he led to worldwide success. As of 2022, he is still Capcom CEO. 

\textbf{Poo} (\textbf{Noritaka Funamizu}, \begin{CJK}{UTF8}{min}船水 紀孝\end{CJK}): Joined Capcom in 1985 where he was a planner on CPS-1 titles Forgotten Worlds, U.N. Squadron , Dynasty Wars, and 1941: Counter Attack. He is also credited with "Special Thanks" for virtually every Capcom hit, including Final Fight and all versions of Street Fighter II. He eventually became a General Producer and worked on numerous Street Fighter titles. In 2004, he left Capcom to help found Crafts \& Meister.

\textbf{Akiman} (\textbf{Akira Yasuda}, \begin{CJK}{UTF8}{min}安田 朗\end{CJK}): Joined Capcom in 1985. As a junior artist he was in charge of background on Hyper Dyne Side Arms. After reportedly asking for a promotion in a washroom encounter, he became a planner (focusing on artwork) for Forgotten Worlds, Final Fight, and Street Fighter II. He dedicated himself to artwork for several Capcom titles well after the days of CPS-1. He left Capcom in 2003 and became a freelance artist.

\textbf{Nin} (\textbf{Akira Nishitani}, \begin{CJK}{UTF8}{min}西谷 亮\end{CJK}): Joined Capcom in 1985. His nickname, "NiN", is well known since it is associated with high-scores in all the games he planned. Among many other titles, he was a planner (focusing on gameplay) on Forgotten Worlds, Final, and Street Fighter II. He left Capcom in 1995 to found Arika and produced the Street Fighter EX series for his former company.

\textbf{Professor F} / \textbf{Arthur King} (\textbf{Tokuro Fujiwara}, \begin{CJK}{UTF8}{min}藤原 得郎\end{CJK}): Joined Capcom in 1983 and planned Commando, Ghosts 'n Goblins, and Bionic Commando. He became General Manager in 1988. After working at Capcom for 13 years, he left in 1996 to start his own studio, Whoopee Camp.

\textbf{Kouichi Yotsui} (\begin{CJK}{UTF8}{min}四井浩一\end{CJK}): Joined Capcom in 1986 and planned the impressive first CPS-1 title, Strider. He left in 1990 and went on to work at Takeru and later Mitchell Corporation. Nowadays, he works as a freelancer.

\textbf{Yoshiki Okamoto} (\begin{CJK}{UTF8}{min}岡本 吉起\end{CJK}): Joined Capcom in 1984 after leaving Konami. We was a planner on early titles such as Side Arms and Willow before he moved to overseeing all arcade development at Capcom, becoming a producer. He is credited with recruiting Akiman which had a profound impact on the arcade division. He left Capcom to start his own video game development company, Flagship. In later years, he created several successful mobile games such as Dragon Hunter and Monster Strike.   

\textbf{Takashi Nishiyama} (\begin{CJK}{UTF8}{min}西山隆志\end{CJK}): Joined Capcom in 1986 coming from Irem where he designed Kung-Fu Master. He was a planner on pre-CPS-1 games, in particular Street Fighter 1 for which he created the special move "Hadouken". He joined SNK in 1990 where he worked on Fatal Fury before becoming a producer on several iterations of King of Fighters and Metal Slug.


\textbf{Yoko Shimomura} (\begin{CJK}{UTF8}{min}下村 陽子\end{CJK}): Joined Capcom in 1988, straight after graduating from Osaka College of Music. She contributed to the soundtrack of over sixteen games starting on console titles before moving to arcades. She is noteworthy for writing the musics of Street Fighter II and Final Fight. She left Capcom in 1993 to work for Square where she is still employed as of 2022.

\textbf{Yoshihiro Sakaguchi} (\begin{CJK}{UTF8}{min}坂口 由洋\end{CJK}): Joined Capcom in 1984. He composed music for both home consoles with titles such as Mega Man and Mega Man 2 and also arcades where he worked on Street Fighter 1 and Final Fight. He left Capcom in the mid 90's.